Jaccard distances for VDJ data
========================================================
Load the necessary functions and data:

```{r step}
knit_hooks$set(webgl = hook_webgl)
source('../../jaccard_distances.R')
load("../../species_by_sample.RData")
```

We create the lists of samples (both patients + controls and just patients):

```{r data prep}
samples.all <- colnames(species)
accn.all <- sapply(samples.all, substr, 1, 8)
samples.patients <- samples.all[5:length(samples.all)]
accn.patients <- accn.all[5:length(accn.all)]
```

We then rarefy the species data to compensate for the overabundance of reads
in certain samples (GTSP0028.1, for instance) to a uniform 300,000 reads/sample.

```{r rarefy}
s <- rrarefy(t(species), 300000)
species <- t(s)
```
Abundance-weighted Jaccard distance, all samples:

```{r awj.all, webgl=TRUE}
# Generate pairwise abundance-weighted (.awj) or unweighted (.uwj) Jaccard
# distances for all samples and just patients
pw.awj.all <- PairwiseJaccardDistance(samples.all, species, weighted=T)
DistanceHeatmap(pw.awj.all, na.diag=T, 
                 main="Abundance-weighted Jaccard Distance")
pc.awj.all <- DistancePCoA(pw.awj.all)
PCPlot3D(pc.awj.all, 
                 main="Abund. Jaccard Distance: Principal Coordinates")
```

Unweighted Jaccard distance, all samples:

```{r uwj.all, webgl=TRUE}
pw.uwj.all <- PairwiseJaccardDistance(samples.all, species, weighted=F)
DistanceHeatmap(pw.uwj.all, na.diag=T, main="Unweighted Jaccard Distance")
pc.uwj.all <- DistancePCoA(pw.uwj.all)
PCPlot3D(pc.uwj.all, main="Jaccard Distance: Principal Coordinates")
```

Abundance-weighted Jaccard distance, patients only:

```{r awj.patients, webgl=TRUE}
pw.awj.patients <- PairwiseJaccardDistance(samples.patients, species, 
                                           weighted=T)
DistanceHeatmap(pw.awj.patients, na.diag=T, 
                 main="Abund. Jaccard Distance Between Patients")
pc.awj.patients  <- DistancePCoA(pw.awj.patients)
PCPlot3D(pc.awj.patients, color.by="accn",
                 main="Abund. Jaccard btwn Patients: Principal Coordinates")
```

Unweighted Jaccard distance, patients only:

```{r uwj.patients, webgl=TRUE}
pw.uwj.patients <- PairwiseJaccardDistance(samples.patients, species,
                                           weighted=F)
DistanceHeatmap(pw.uwj.patients, na.diag=T, 
                 main="Jaccard Distance Between Patients")
pc.uwj.patients <- DistancePCoA(pw.uwj.patients)
PCPlot3D(pc.uwj.patients, color.by="accn",
                 main="Jaccard btwn Patients: Principal Coordinates")
```

